### 2016-05-18 paper/paper.tex
Section on difficulty adjustment

>>>>

\subsubsection{Difficulty Adjustment}

The difficulty of proof-of-work changes dynamically in DDoSCoin, as it does in
other crypto-currencies, in order to limit the rate at which new blocks are mined.
However, in DDoSCoin, the difficulty is adjusted separately for each target domain. 
The difficulty is not global, since domains could have different maximum throughputs, 
allowing more or fewer connections from all miners over the same time period. Consider
a single domain that handles many connections per second added to the target list. 
The miners would connect to that server more often, since it will give more chances 
at mining a block, and thus relieve traffic from the other targets.

DDoSCoin adjusts diffuculty for a given domain as a function of the total number 
of blocks mined, rather than the number of blocks mined by targetting that domain. 
This allows target domains that somehow become more difficult to reach to quickly 
return to a more appropriate difficulty, without having many blocks mined at the 
high difficulty. This comes at a sacrifice to the agility of corrections when a 
domain has too low of a difficulty. This allows a run on an easily mined domain 
to occur for longer.

We correct for this lower reactivity by dividing the number of blocks required 
for a difficulty adjustment by the number of domains being targeted. Thus, as 
more domains are in the target list and it becomes more likely that one may
be able to handle many requests, the total number of mined blocks that will result
in difficulty adjustment shrinks.

A target's initial difficulty in DDoSCoin is decided by the stakeholder that
introduces the target in a proof-of-stake block. The stakeholder is incentivized to not
set the difficulty too low, as the DDoS would be innefective. Also, many coins would be
mined quickly, devaluing the stakeholder's own coins. If the difficulty is set too high,
there will be a delay as other domains are mined, and the difficulty adjusts down
to the appropriate level.
